---
title: "Simple One to One Binding: Simulation"
author: "Ren-Huai Huang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Simple one to one model:  
<font size = "3">
$A + L \overset{k_{on}}{\underset{k_{off}}\rightleftarrows} AL\;\; (K_d = k_{off}/K_{on})$  

* A: the protein to be analyzed. 
* L: Ligand immobilized on the pin
* AL: Complex formed on the pin

*Below is the rate equation:*    

${d[AL] \over dt} = k_{on}  [A]  [L] - k_{off}  [AL]$

* other forms: 

    + ${dy \over dt} = k_{on} [conc] (R_{max} - R) - k_{off}  y$  

    + ${dy \over dt} = k_{on} [conc] R_{max} - (k_{on} [conc] + k_{off})  y$ 

    + ${dy \over dt} = k_{on} C R_{max} - (k_{on} C + k_{off})  R$ 

* Parameters:

    + Response (nm): $R = [AL] = y$    
    + Ligand on the sensor: $[L] = R_{max} - R$  
    + Conc. of the analytes: $C = [conc] = [A]$  
    + $R_{max} = [AL] + [L]$   
    
</font>
-----
    
```{r, echo = FALSE, results = FALSE, message = FALSE}
knitr::opts_chunk$set(fig.width=6.5, fig.height = 4)
require(reshape2); 
require(ggplot2);
require(grid)

require(pldfit)
```    
## Simulation & Plot
```{r}
# simulate the data use the following parameters
par = list(kon    = 2e2, 
           koff   = 1e-2, 
           rmax   = 1,
           concs  = 1e-5 * (2^(0:5)),
           time   = seq(0, 300, length.out = 1501),
           t2     = 150)

# simulation
model = "simple1to1"
xySimulated <- kinsim(par = par, model = model, noise = 0.01) 

# plot the simulation
# ySimulated$Time = time; 
xy <-reshape2::melt(data = xySimulated, 
                     id.vars = "Time", 
                     measure.vars = rev(1:6), 
                     variable.name = "Conc")

g <- ggplot()  + xlab("Time (sec)") + ylab("Response (nm)") +
    labs(linetype= 'title') + 
    ylim(-0.025,1) + 
    theme_classic() + 
    theme(legend.position=c(0.9, 0.65), 
          legend.text=element_text(size = rel(1)), 
          legend.key.size=unit(0.9,"line")); 
g <- g + geom_line(data = xy, aes(x = Time, y = value, color = Conc)); 
print(g)
```

## Kinetic Fitting
```{r}

# init
initPar_test = list(kon =1, koff = 1, rmax = 1)  
lower        = list(kon =1e-04, koff=1e-04, rmax = 0.01);
upper        = list(kon =1e04,  koff=1e04,  rmax = 10);
t2  = par$t2 # t2 is the beginning of the diassociation.  
concs        = par$concs 
dat          = xySimulated 

# Fit
fit <- kinfit(par = initPar_test, 
              lower = lower, 
              upper = upper, 
              dat = dat, 
              concs = concs, 
              t2 = t2, 
              model = "simple1to1")
names(fit)
class(fit)
par[1:3] # simulation parameters
fit$par[1:3] # paramenters after fitting
cbind(simulation= par, init = initPar_test, fitting = fit$par)

#prodict and plot

predFit <- predict(fit, concs)
predFit <- reshape2::melt(predFit, id.vars = "Time")
g + geom_line(data=predFit, aes(x = Time, y = value, group = variable) ) 


```

## Equilibrium Fitting
```{r}
# 
dat    = xySimulated
concs  = par$concs
scale  = 1e3
fit <- ssgfit(datF = dat, 
              concs = concs * scale,  
              start = list(Rmax = 0.5, Kd=1),
              width = 5,
              t2    = 149.5,
              model = "simple1to1")
coef(fit)
with(par, koff/kon *scale)
plot(fit$datF[1:2])
par$concs * scale
lines(fit$predict, lty = 2)
class(fit)
plot(fit)

```

